---
title: "toy_play"
author: "David Gerard"
date: "`r Sys.Date()`"
output: workflowr::wflow_html
---

## Introduction

I try to find some weeknesses in current methods that cluster rankings.

## Analysis

Some tricky data. My idea is that individuals 1 and 2 are the only thing that distinguish the two groups. So we should cluster people in one group is 1 > 2 and in the other group if 2 > 1. We will leave some groups to have missing values of 1 and 2

```{r}
source("./code/trick_gen.R")
nobj <- 8
nind <- 500
pmiss <- 0.1
dat <- gen_12diff(nobj = nobj, nind = nind, pmiss = pmiss)
```


```{r, warning=FALSE}
library(Rankcluster)
```

```{r, eval = FALSE}
rout <- rankclust(data = dat)
save(rout, file = "../output/first_rout.RData")
```

```{r}
load("./output/first_rout.Rdata")
```


Only one cluster is estimated.
```{r}
rout@K
```

So I'll force it to be $K = 2$
```{r, eval = FALSE}
rout2 <- rankclust(data = dat, K = 2)
save(rout2, file = "../output/second_rout.RData")
```

```{r}
load("./output/second_rout.Rdata")
```

There is some power to distinguish the two groups. Also, most rankings have a high probability of being in one of the two groups, which is weird. We wouldn't think to see this.
```{r}
library(ggplot2)
prob1 <- rout2@results[[1]]@tik[, 1]
trueclust <- rep(c(1, 2), each = nind / 2)
qplot(as.factor(trueclust), prob1, geom = "boxplot") +
  theme_bw()
```

Compare to gold standard where we know the grouping criterion. The best we could do is say 40% are in each group, and 20% half probability 1/2 of being in either group.

```{r}
sum(dat[, 1] > dat[, 2], na.rm = TRUE) / nrow(dat)
sum(dat[, 2] > dat[, 1], na.rm = TRUE) / nrow(dat)
sum(is.na(dat[, 2]) | is.na(dat[, 1])) / nrow(dat)
```






